\\Large Rising temperatures alter how and where boreal mammals move

### 2025-11-03 writing/manuscript.Rmd
add ref for RS's cougar data; add missing `\beta_0`

\noindent Boreal caribou and wolf telemetry data were acquired from a data repository of the British Columbia Oil and Gas Research and Innovation Society (BC ORGIS) that was collected as part of the boreal caribou radio-collaring program of the BC OGRIS Research and Effectiveness Monitoring Board [REMB$;$ @bc_ogris_boreal_2018]. Southern mountain caribou data were obtained from @ford_effects_2023. Cougar data are from @darlington_southern_2025 and @serrouya_ref. Elk data from the work of @ciuti_human_2012 were downloaded from Movebank [@kays_movebank_2022]. Finally, grizzly bear telemetry data are from @grizzly_ref, while mountain goat data are from the work of @balyx_human_2022 and were provided by the British Columbia Ministry of Environment and Parks.

@@

\begin{equation}\label{eq:hrsf}
\begin{cases}
O \sim \text{Pois}(\lambda) \\
\mathbb E(O) = \mathbb V(O) = \lambda \\
\begin{aligned}
\text{log}(\lambda) = & f_{1}(\texttt{forest\_perc}) + f_{2}(\texttt{elevation\_m}) + f_{3}(\texttt{dist\_water\_m}) + \\
& Z_\texttt a + f_{4, \texttt{a}}(\texttt{forest\_perc}) + f_{5, \texttt{a}}(\texttt{elevation\_m}) + f_{6, \texttt{a}}(\texttt{dist\_water\_m}) + \\
& f_{7}(\texttt{forest\_perc}, \texttt{temp\_c}) + f_{8}(\texttt{elevation\_m}, \texttt{temp\_c}) + \\
& f_{9}(\texttt{dist\_water\_m}, \texttt{temp\_c}) + f_{10}(\texttt{temp\_c}) + f_{11,\texttt a}(\texttt{temp\_c}))
\end{aligned}
\end{cases},
\end{equation}

>>>>

\noindent Boreal caribou and wolf telemetry data were acquired from a data repository of the British Columbia Oil and Gas Research and Innovation Society (BC ORGIS) that was collected as part of the boreal caribou radio-collaring program of the BC OGRIS Research and Effectiveness Monitoring Board [REMB$;$ @bc_ogris_boreal_2018]. Southern mountain caribou data were obtained from @ford_effects_2023. Cougar data are from @darlington_southern_2025 and @serrouya_ref. Elk data from the work of @ciuti_human_2012 were downloaded from Movebank [@kays_movebank_2022]. Finally, grizzly bear telemetry data are from @serrouya_grizzly_2011, while mountain goat data are from the work of @balyx_human_2022 and were provided by the British Columbia Ministry of Environment and Parks.

@@

\begin{equation}\label{eq:hrsf}
\begin{cases}
O \sim \text{Pois}(\lambda) \\
\mathbb E(O) = \mathbb V(O) = \lambda \\
\begin{aligned}
\text{log}(\lambda) = & \beta_0 + f_{1}(\texttt{forest\_perc}) + f_{2}(\texttt{elevation\_m}) + f_{3}(\texttt{dist\_water\_m}) + \\
& Z_\texttt a + f_{4, \texttt{a}}(\texttt{forest\_perc}) + f_{5, \texttt{a}}(\texttt{elevation\_m}) + f_{6, \texttt{a}}(\texttt{dist\_water\_m}) + \\
& f_{7}(\texttt{forest\_perc}, \texttt{temp\_c}) + f_{8}(\texttt{elevation\_m}, \texttt{temp\_c}) + \\
& f_{9}(\texttt{dist\_water\_m}, \texttt{temp\_c}) + f_{10}(\texttt{temp\_c}) + f_{11,\texttt a}(\texttt{temp\_c}))
\end{aligned}
\end{cases},
\end{equation}
